How Slow do my Transient Typechecks Go?

### 2019-08-17 paper.tex
Edit pass through S5 Individual Annotations

The column graphs show the execution time of configurations with with only a single type annotation, the x-axis indicates the index of this annotation, thus the first column represents the 1\textsubscript{st} annotation, and the last column represents the last one (in the order they appear in the source code). The y-axes for the column graphs are the same as the associated scatter graph. However, though the right y-axes for the column graphs appear to be identical the scatter plot ones, they are relative to performance results collected on different days: this was to ensure that the performance of the test computer had not changed significantly from when the typing lattice experiments where run.

@@

As can bee seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmark, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing lattice graphs. For permute there is actually a signficant performance \emph{incrase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight incrase in performance, but here this is caused by two type annotations (in red and blue), however this does not appear to be comulative (as indicated by the purple dots being about the same height as the red and blue ones).

List is interesting as it demonstrates that the red and blue type annotations both cause a significant decrease in performance, which is even greater when both are present. Richards is particularly od as it shows a performance decrease that appears to occur when the red type annotations is present, but not the blue one.

Finally, SpectralNorm and Json, although we found outliers in the column graphs (types 27 and 83, highlighted in red), we were unable to find a pattern in the typing lattice.

Note however that in the case of DeltaBlue and Richards, there are two noticeable spikes in the column graphs (at \#62 and \#24, respectively), however we found no apparent relation between these and the typing lattice.

>>>>

The column graphs show the execution time of configurations with with only a single type annotation, the x-axis indicates the index of this annotation, thus the first column represents the 1\textsubscript{st} annotation, and the last column represents the last one (in the order they appear in the source code). The y-axes for the column graphs are the same as the associated scatter graph. However, though the right y-axes for the column graphs appear to be identical the scatter plot ones, they are relative to performance results collected on different days: this was to ensure that the performance of the test computer had not changed significantly from when the typing lattice experiments were run.

@@

As can be seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmark, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing lattice graphs. For Permute there is actually a signficant performance \emph{increase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight increase in performance, but here this is caused by two type annotations (in red and blue); this does not appear to be cumulative, however, as the purple dots are around the same height as the red and blue ones: \textit{either} annotation is sufficient for the full improvement.

List is interesting as it demonstrates that the red and blue type annotations both cause a significant decrease in performance, which is even greater when both are present. Richards is particularly odd as it shows a performance decrease that appears to occur when the red type annotations is present, but not the blue one.

Finally, for SpectralNorm and Json, although we found outliers in the column graphs (types 27 and 83, highlighted in red), we were unable to find a pattern in the typing lattice.

Note however that in the case of DeltaBlue and Richards, there are two noticeable spikes in the column graphs (at \#62 and \#24, respectively); nonetheless, we found no apparent relation between these and the typing lattice.
